Creating optimal conditions for reproducible data analysis in \R with `fertile'\protect\thanks{The authors gratefully acknowledge contributions from Hadley Wickham, Jenny Bryan, Greg Wilson, Edgar Ruiz, and other members of the \pkg{tidyverse} team.}

### 2020-08-04 STAT-paper-template/APA/fertile.Rnw
close #5

A much more effective way of realizing widespread reproducibility is to make the process for doing so simple enough that it takes little to no conscious effort to implement.

>>>>

A more effective way of realizing widespread reproducibility is to make the process for doing so simple enough that it takes little to no conscious effort to implement. You want users to "fall into a hole"\footnote{We paraphrase Hadley Wickham.} of good practice.
